\subsection{Hardware}
The Eye Tribe eye tracking device will be used as the primary eye tracking recording device for this project. The Eye Tribe eye tracking device connects to the computer through a USB 3.0 port and as such it is required that the computer the application would be running on has USB 3.0 ports. The Machine must also have the ability to connect to the internet via either a wired or wireless connection to ensure that The Eye Tribe recording server can be run.

\subsection{Operating System}
The application only supports installation on computers running a Microsoft Windows operating system. The application may work on both 32-bit and 64-bit systems but 64-bit systems with large amounts of memory are recommended for memory processing. 

\subsection{Additional Software}
You need to have the .Net 4.0 Framework installed or better to run the program. This ensures that all the current technologies are used properly and to the best of their ability. The Eye tribe SDK will also need to be so that the camera can be calibrated and data can be transferred to the program.

\subsection{Version Control Management}
GitHub will be used to as the version control management system for the duration of this project.
This is a distributed version control meaning that every node has a copy of the repository. With this tool we can easily track issues and bug fixes throughout the program as well as manage new features and testing with the use of branches.

\subsection{Development Environment}
The application will be programmed in the C sharp(C\#) programming language through Microsoft Visual Studio 2013 Community Edition. This is a free version of Microsoft's Visual studio and is built for small development teams such as up to five members. The additional software (namely The Eye Tribe SDK) being used also provides C\# libraries that can be used to access additional features and capabilities of their software and hardware.
