\subsection{Singleton}
The program uses a server to gather the data from the eye tracking camera.This server is constantly running and there should only be one instance of this class running so that we do not have multiple servers running and all the data is pulled consistently.The server will then need to follow the singleton design pattern.The singleton design patter is a creational design pattern that is used when only one instance of the object is created at most.This will provide the solution of only one server object being created at time.The object is referenced and is not recreated and therefore there is only one instance of the class.The singleton is simplistic in nature as it is only one object that has a reference to itself.
\subsection{Extensibility pattern}
The program is comprised of many different modules.The different modules will need to work together to perform all the tasks that the program is required to carry out.The extensibility pattern helps to achieve this.The extensibility pattern provides a framework for the inclusion of other modules into the program.This is achieved through C\# and its ability to create DLL(Dynamic Link library) and then using them in a other solution.This allows us to add functionality at a later stage and will also allow the fixing and enhancing of the application at a later stage.This means that modules can easily be added and removed from the system
\subsection{Flyweight}
The program has data that needs to be shared amongst modules and that also needs to be used throughout the system.This is achieved by the flyweight pattern which allows data to be shared amongst the different modules.The value of settings and certain program variables.This variables are static and are defined as internal so that only the program can access the values.This ensures that all the modules are able to share the memory and save memory as well as processing speed.

\subsection{Model-View-Controller} 
\begin{flushleft}
The project can easily be split as: User, Interface and, Background Calculations. The user interacts with the Interface, the program that will be executed, handling the eye tracking. The interface will convert the received data into a format that the data processing section can work with. The data processing section will take render out/back the heat maps generate from the users focus.

It is with this in mind that the Model-View-Controller(MVC) design pattern will be used.
The MVC separates the data model, user interface, and control logic which is exactly what we want. We want the user to be able to use our system without having to know how it works. Only the basics should be available i.e record, printing out texture/model.
\end{flushleft}