We have chose the following technologies carefully as they incorporate into one another to form a sound basis for our project to operate on.

\begin{itemize}
	\item \textbf{C\#}:	C\# is a programming language that was designed and developed by Microsoft.The language is a object orientated language and is highly focused on component-oriented. C\# is used with the .NET frame work which was discussed in a earlier section. The language is a very versatile language that is used when developing most Microsoft projects. The language is able to create classes and a GUI which allows us to map certain functions of the GUI to the class.
	
	\item \textbf{Eye Tribe eye-tracker}: This is one of the cheapest if not the cheapest eye tracking cameras available on the market.The tracker is infra-red eye tracker which can track gaze data and then this data can be used to carry out numerous functions.The Eye tribe eye tracker can be used on a computer or a mobile device such as a smart phone.The eye tracker is \$99 eye tracker that makes it cheap and competitive with the more expensive ones on the market.
	
	\item \textbf{Eye tribe SDK}: This is a full SDK that is used to develop programs that will use the Eye-tribe tracking camera. The SDK comes with the user interface and server components to help design new programs that are compatible with the eye tribe software.
	
	\item \textbf{GitHub}: This is a version control system that is used to manage the versions of software.Github uses a copy-modify-merge system where the users will clone a repository and then modify it and then merge it. It is a distributed version control so every person has copy to the repository.
		\item \textbf{NuGet}: This is a packet manager which helps to manage all the packages in a project. This allows users to add packages from all sources to their projects to use certain parts of it.This also manages the packages so that you don't have to worry about locating them and referencing them.
		\item \textbf{Nunit}: This is a testing framework built for the .Net framework.This is very similar to java's JUnit. The same premise and method is used to create and execute tests. The tests will show a positive result if they have passed.If a failure occurs on a test it will tell you where and what cause the error. NUnit is used to write unit tests so that each part of a project is tested.
		
		\item \textbf{OpenTK}: OpenTK or Open Toolkit Library is a OpenGL library that allows the users to manipulate 3D models inside a .Net projects such as a C\# project. This means that a 3D model can then be manipulated and used in a program.
		
		\item \textbf{Visual Studio Community 2013}: Visual Studio Community 2013 is a robust IDE used to write .NET projects such as a C\#  project.The IDE has many features that help improve development and increase productivity. The Visual Studio community edition is free to developers if you sign up with a Microsoft account.
\end{itemize}