\subsection{Description of Document}
This document aims to show the design processes used to create the NTT Eye-Tracking application. The document is divided into three sections. Each section describes a certain aspect about the design of the software and how the underlying structure and interfaces are combined to create the final product. The purpose of this eye-tracking software is to allow the user to track eye movements on different kinds of media types and models. This is something that has not been done on models such as three dimensional and video models as yet and will be a great contribution to the eye-tracking community. 

\subsection{Section Overview }
The three sections that are as follows:
\begin{itemize}
\item Data Design.
\item Interface Design.
\item Procedural Design.
\end{itemize}

These three sections each cover a very important part this software application. Data design will explain the structures used with in the software and how each one works with the other. Interface design will describe the choices made for the look of the software while still incorporating user experience goals to make the program as user friendly as possible. Procedural Design will focus on the procedures and functionality used through out the application.\\
\\
Take special note that Architectural Design is not included with in this document. This is not necessary as the topics that would be covered by the already existing architectural requirements document. Please refer to it for further information about design structures and such.